The Unicode Cookbook \linebreak for Linguists

### 2018-07-31 book/chapters/ipa_meets_unicode.tex
typo in Chapter 5

There are several pitfalls to be aware of when using the Unicode Standard to
encode IPA.\@ As we have said before, from a linguistic perspective it might
sometimes look like the Unicode Consortium is making incomprehensible decisions,
but it is important to realize that the consortium has tried and is continuing
to try to be as consistent as possible across a wide range of use cases, and it
does place linguistic traditions above other orthographic choices. Furthermore,
when we look at the history of how the IPA met Unicode, we see that many of the
decisions for IPA symbols in the Unicode Standard come directly from the
International Phonetic Association itself. Therefore, many pitfalls that we will
encounter have their grounding in the history of the principles of the IPA, as
well as in the technological considerations involved in creating a single
multilingual encoding. In general, we strongly suggest to linguists to not
complain about any decisions in the Unicode Standard, but to try and understand
the rationale of the International Phonetic Association and the Unicode
Consortium (both of which are almost always well-conceived in our experience)
and devise ways to work with any unexpected behavior.

>>>>

There are several pitfalls to be aware of when using the Unicode Standard to
encode IPA.\@ As we have said before, from a linguistic perspective it might
sometimes look like the Unicode Consortium is making incomprehensible decisions,
but it is important to realize that the consortium has tried and is continuing
to try to be as consistent as possible across a wide range of use cases, and it
does not place linguistic traditions above other orthographic choices. Furthermore,
when we look at the history of how the IPA met Unicode, we see that many of the
decisions for IPA symbols in the Unicode Standard come directly from the
International Phonetic Association itself. Therefore, many pitfalls that we will
encounter have their grounding in the history of the principles of the IPA, as
well as in the technological considerations involved in creating a single
multilingual encoding. In general, we strongly suggest to linguists to not
complain about any decisions in the Unicode Standard, but to try and understand
the rationale of the International Phonetic Association and the Unicode
Consortium (both of which are almost always well-conceived in our experience)
and devise ways to work with any unexpected behavior.
